%
% Author: Elijah C. Voigt
% Filename: resume.tex
% Make: pdflatex resume.tex # produces resume.pdf
% Description: A resume!
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.
%

\include{header}

\begin{document}
%
% Name, Email, Location
%
\begin{tabular}[t]{l@{}}
  \textbf{\Huge{Elijah Caine M. Voigt}}
\end{tabular}
\hfill
\begin{tabular}[t]{r@{}}
    \normalsize{elijah.caine.mv@gmail.com} \\
    \normalsize{http://elijahcaine.me} \\
    % \normalsize{Pacific Northwest, USA} \\
    \normalsize{(971) 533 5545}
\end{tabular}

% Overview
\skill{\$ whoami}

\begin{description}
  \item My career interests are in creating and improving \textbf{Open Source solutions} to common problems, \textbf{presenting talks} on interesting topics, and \textbf{automating} the boring stuff with \textit{security} and \textit{efficiency} in mind. I love talking about:
  \item \overview{Server-side Dev}{Linux (Debian, Ubuntu, RedHat, Fedora, Amazon), Python, Django, Golang, Rust, Ruby, NodeJS}
  \item \overview{DevOps}{Kubernetes, Terraform, Chef, Ansible, Docker, AWS, Azure, GCP, Digital Ocean, Git \& GitHub}
  \item \overview{Open Source}{Publish general purpose tools, improve existing code-bases, document upstream projects.}
  \item \overview{Leadership}{Linux Users Group president, taught DevOps BootCamp, SCaLE conference speaker.}
\end{description}

% Emplolyment history
\skill{\$ jobs}
\subskill{CloudBolt Software}{Portland, OR}{Software Engineer}{04/2019 - Present}{
  \begin{itemize}
    \skitem{Python}{Develop integrations with cloud APIs, managed services, and CLI tooling.}
    \skitem{Django}{Contribute to legacy and green-field (new) Django + Django Rest Framework-based products.}
    \skitem{Tooling}{Maintained and improved internal tooling, CICD pipelines, and customer-facing software packages.}
  \end{itemize}
}

\subskill{Nordstrom Technology}{Seattle, WA}{Linux DevOps (Engineer 2)}{06/2017 - 08/2017, 02/2018 - 04-2019}{
  \begin{itemize}
    \skitem{CI-CD}{Lead OS image building pipeline project; huge reduction of tech-debt, launched w/in 3 months of kickoff.}
    \skitem{DevOps}{Written and maintained Chef cookbooks for Linux software; contributed to Open Source cookbooks.}
    \skitem{Monitoring}{Evaluated monitoring solutions; migrated existing monitoring/alerting to Prometheus and DataDog.}
  \end{itemize}
}

\subskill{CoreOS}{San Francisco, CA/Remote}{Documentarian}{09/2016 - 05/2017}{
  \begin{itemize}
    \skitem{Community support}{Helped users in Slack and IRC, answering beginner to intermediate questions.}
    \skitem{Open source docs}{Reviewed, tested, and contributed to public facing developer-focused docs.}
  \end{itemize}
}

\subskill{Oregon State University Open Source Lab}{Corvallis, OR}{Software Developer}{05/2014 - 09/2016}{
  \begin{itemize}
    \skitem{Efficiency}{Decreased time-to-deployment by integrating Docker into the testing/development workflow.}
    \skitem{Mentorship}{Taught new developers fundamental ``real-world'' work skills like git and framework use.}
    \skitem{Development}{Helped design and implement TimeSync, a time-tracking API for work logging.}
  \end{itemize}
}

% Education history
\skill{\$ history}
\subskill{BSCS - Oregon State University}{Corvallis, OR}{Undergraduate (GPA 3.53)}{09/2013 - 12/2017}{
  \begin{itemize}
    \skitem{Major: Computer Science}{Coursework included Operating Systems I/II, Software Engineering I/II, Defense Against the Dark Arts, Programming Languages, Data Structures, Databases, Web Development, and three term a Capstone Project with the Apache Software Foundation.}
    \skitem{Minor: Mathematics \& Security}{Coursework included Cryptography I,  Linear Algebra, Numerical Analysis, Computational Number Theory, and a self guided course on Advanced Topics of Cryptography.}
  \end{itemize}
}

\skill{\$ more}
\subskill{OSU Linux Users Group}{}{President}{09/2014 - 09/2017}{
  \begin{itemize}
    \skitem{Scheduled speakers}{Coordinated industry professionals and Alumni from IBM, Nordstrom, CoreOS, Mozilla, and Google to speak, recruit, and eat pizza at weekly meetings.}
    \skitem{Planned weekly meetings}{Recruited members to present on OpenSource/Libre Software topics.}
    \skitem{URL}{\texttt{https://lug.oregonstate.edu}}
  \end{itemize}
}

\subskill{Southern Annual Linux Expo}{Los Angeles, CA}{Speaker}{03/2018}{
  \begin{itemize}
    \skitem{Presented}{Presented ``Crypto: Practical Math'', a talk about concepts in advanced Cryptography without the tedious math that usually comes with it.}
    \skitem{URL}{\texttt{https://youtu.be/ddeV3pESy3Y?t=2h10m4s}}
  \end{itemize}
}

\subskill{DevOps BootCamp}{}{Educator}{09/2014 - 06/2015}{
  \begin{itemize}
    \skitem{Lectured}{Co-presented weekly topics for students and mentored those who struggled with the material.}
    \skitem{Designed curriculum}{Improved curriculum based on student feedback to support online students.}
    \skitem{URL}{\texttt{https://devopsbootcamp.osuosl.org}}
  \end{itemize}
}

\subskill{elijahcaine.me}{}{Administrator}{05/2014 - Present}{
  \begin{itemize}
    \skitem{Management}{Configure, deploy, and manage applications on my personal domain using Kubernetes, Google Cloud Platform, DigitalOcean, Docker, LetsEncrypt, and NGINX. e.g., \texttt{https://elijahcaine.me}}
  \end{itemize}
}

\vspace{10pt}
\centerline{1009 B899 9401 526E 33C5  BA8B 694C A211 7443 799C}

\end{document}
